A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-07-15 natural history of scavenging.tex
whale reference added

\textcolor{blue}{The physical differences between water and air mean carcass availability is radically different between these environments \citep{beasley2012carrion}. 
For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers.
Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers \citep{beasley2012carrion}. 
Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass \citep{moleon2015living}. 
The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.}
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.
So, despite being unlikely, the energetic feasibility of a marine scavenger that specialises on large carcasses has a long history.

Perhaps the greatest environmental driver of scavenging tendency is that of temperature. 
his has a significant bearing on the availability and persistence of carrion.
We know from the geological record shows that the Earth has undergone radical fluctuations in temperature over time.
\textcolor{blue}{On land, there are a wide variety of vegetation types, from thickly forested areas to open grassland and the extent of this vegetation changes with season.}
All of these factors influence the availabiltiy of carrion.  
Moreover, oceanic productivity is also impacted by climactic conditions.

@@

>>>>

\textcolor{blue}{The physical differences between water and air mean carcass availability is radically different between these environments \citep{beasley2012carrion}. 
For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers.
Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers \citep{beasley2012carrion}. 
\textcolor{blue}{Research has shown that an animal need only travel 36 km to encounter a fresh whale carcass \citep{smith2003ecology}.} 
The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.}
\cite{ruxton2005searching} argued that although this is energetically feasible it's ecologically unlikely.
Any animal that could find such whale carcasses is unlikely to have ignored other types of carrion.
Although no aquatic species have ever exceeded the size of whales, some enormous animals have evolved in this environment before the evolution of cetaceans, including \textit{Leedsichthys}, a bony fish from the Middle Jurassic (174.1 - 163.5 Mya) and the aquatic Mesozoic reptiles, the plesiosaurs, pliosaurs and ichtyosaurs, that could all exceed 15 metres in length \citep{ruxton2011zoology,danise2014ecological}.
So, despite being unlikely, the energetic feasibility of a marine scavenger that specialises on large carcasses has a long history.

Perhaps the greatest environmental driver of scavenging tendency is that of temperature. 
This has a significant bearing on the availability and persistence of carrion.
We know from the geological record shows that the Earth has undergone radical fluctuations in temperature over time.
\textcolor{blue}{On land, there are a wide variety of vegetation types, from thickly forested areas to open grassland and the extent of this vegetation changes with season.}
All of these factors influence the availabiltiy of carrion.  
Moreover, oceanic productivity is also impacted by climactic conditions.

@@

%Carcass size shapes the structure and functioning of an African scavenging assemblage
%Moleon et al
%We found strong evidence indicating that carcass size is a major factor governing the associated scavenger assemblage. Scavenger species richness per carcass and carcass consumption time and rate increased with carcass size, while carcass detection time and percentage of carrion biomass consumed were negatively related to carcass size. 
%During the dry season, less vegetation cover might also favor the detection of carrion by scavengers, especially mammals (Ruzicka and Conover 2012).
%The mean number of scavenger species exploiting a particular carcass increased with carcass size, probably because the longer temporal availability and higher conspicuousness of larger carcasses (DeVault et al. 2004) allowed more species to aggregate.
%This suggests that hyenas were involved in some interactions that enhance community structure, such as carcass signaling and tearing open of thick-skinned animals (Moleón et al. 2014a).
